master thesis

### 2018-03-25 Paper - Latex/Paper - Skizze - v4.tex
more data

    Parsimony methods are simple methods in which you can not include information such as branch 
      length (development time of the species). This is also their main point of criticism compared to 
      the more complex likelihood based models. Since there are no branch lengths or other information 
      available for the present relationship tree, and thus can not take advantage of the 
      other models, we decided in favor for parsimonious. \\

@@

    The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
      Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
    Since the analysis of the tree is not part of this work, it should be mentioned here that, 
      according to recent findings, this is not complete and we lack some taxa in every rank. For 
      example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
      \cite{CavalierSmith1981}. \\
    In section \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\

    Also, the global database is not fallible. We found out (section x) that there is some 
      misinformation. \\
    We were able to report some of these directly to Globi.

>>>>

    Parsimony methods are simple methods in which you can not include information such as branch 
      length (development time of the species). This is also their main point of criticism compared to 
      the more complex likelihood based models. Since there are no branch lengths or other information 
      available for the present relationship tree, and we thus can not take advantage of the 
      other models, we decided in favor for parsimonious. \\

@@

    The investigation of the taxonomy revealed that the OTL tree has three kingdoms: Chloroplastida, 
      Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
    Since the analysis of the tree is not part of this work, it should be mentioned here that, 
      according to recent findings, this is not complete and we lack some taxa in every rank. For 
      example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
      \cite{CavalierSmith1981}. \\
    In \colorbox{red}{section/page} \pageref{subsec:listPhyla} of the appendix is a list of all phyla. \\

    Also, the global database is not infallible. We found out (section \colorbox{red}{x}) that there is some 
      misinformation. \\
    We were able to report some of these directly to Globi.
